---
title: "Formative Assessnent 2"
author: "Vera Aguila"
date: "2024-02-18"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Probablity of getting 50%

1. Use R to illustrate that the probability of getting:
  + a head is 0.5 if a fair coin is tossed repeatedly;
    
Let's say that the coin will be tossed 100 times. So, freq is equal to 100.
```{r coin1}
freq <- 100
coin_toss <- sample (c("H","T"), freq, replace = T)
coin_toss
```
The table shows the results of tossed coin 100 times.

```{r coin2}
table(coin_toss)/freq
```
The table shows the percentage of getting head and tail. We can see that the results are near 0.5 or 50%. Now, let's try again and make the freq bigger.

The probability of getting head or tail with 5,000 toss:
```{r coin3, echo=FALSE}
freq <- 5000
coin_toss <- sample (c("H","T"), freq, replace = T)
```
```{r coin4, }
table(coin_toss)/freq
```
We can see at the table that the probability of getting head are getting nearer to 0.5.We can conclude that if a fair coin is tossed repeatedly, the probability of getting a head is 0.5.




<br><br>
  + a red card is 0.5 if cards are drawn repeatedly with replacement from a well-shuffled deck;
  
  ```{r card}
cards <- rep(c("red", "black"), times = c(26, 26))
freq <- 100000
drawn <- sample(cards, size = freq, replace = T)
get_red <- sum(drawn == "red") / freq
print(paste("Probability of getting a red card:", get_red))
```
<br><br>
  + an even number is 0.5 if a fair die is rolled repeatedly.

  ```{r die}
die <- rep(c("odd", "even"), times = c(3,3))
freq <- 100000
rolled <- sample(die, size = freq, replace = T)
get_even <- sum(rolled == "even") / freq
print(paste("Probability of getting an even number:", get_even))
```

******

## Rolling a die 

3. An experiment consists of rolling a die. Use R to simulate this experiment 600 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting each of 1, 2, 3, 4, 5, and 6.

```{r rdie}
freq <- 600
x <- sample (c(1,2,3,4,5,6), freq, replace = TRUE)
x
```
<br>
Probability of getting one:
```{r rdie2}
get_one <- sum(x==1)/freq
print(paste("Probability of getting one:", get_one))
```
<br>
Probability of getting two:
```{r rdie3}
get_two <- sum(x==2)/freq
print(paste("Probability of getting one:", get_two))
```
<br>
Probability of getting three:
```{r rdie4}
get_three <- sum(x==3)/freq
print(paste("Probability of getting three:", get_three))
```
<br>
Probability of getting four:
```{r rdie5}
get_four <- sum(x==4)/freq
print(paste("Probability of getting four:", get_four))
```
<br>
Probability of getting five:
```{r rdie6}
get_five <- sum(x==5)/freq
print(paste("Probability of getting five:", get_five))
```
<br>
Probability of getting six:
```{r rdie7}
get_six <- sum(x==6)/freq
print(paste("Probability of getting six:", get_six))
```
<br><br>
Let's see if it equals to 1
```{r rdie8}
total<- get_one + get_two +get_three + get_four + get_five + get_six
print(paste("The total is", total))
```
